---
title: "HW 4 Problem 2"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---


```{r setup, include=FALSE}
library(flexdashboard)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(p8105.datasets)
library(plotly)
data("instacart")
janitor::clean_names(instacart)

```

---
Column {data-width=650}
-----------------------------------------------------------------------

### Pie Chart of Top Ten First Product

```{r}
piefilter1 <- instacart %>%
    filter(add_to_cart_order == 1) %>%
    count(product_name) %>%
    mutate(n = factor(n)) %>%
    arrange(desc(n)) %>%
    head (10)

piefilter1 %>%
      plot_ly(labels = ~product_name, values = ~n, 
            type = 'pie')

```

This pie chart looks at the top ten most ordered first items, with bananas being the overwhelming majority. 

Column {data-width=350}
-----------------------------------------------------------------------

### Bar Chart of Order Days

```{r}
days_of_week <- instacart %>%
  select(order_id, order_dow) %>%
  arrange(desc(order_dow)) %>%
  mutate(order_dow = case_when(
    order_dow == 0 ~ "Saturday",
    order_dow == 1 ~ "Sunday",
    order_dow == 2 ~ "Monday",
    order_dow == 3 ~ "Tuesday",
    order_dow == 4 ~ "Wednesday",
    order_dow == 5 ~ "Thursday",
    order_dow == 6 ~ "Friday"
  )) %>%
  count(order_dow)

days_of_week %>%
  plot_ly(x = ~order_dow, y = ~n, color = ~order_dow, 
          type = "bar")

```
This bar chart looks at number of products ordered per day of the week. Saturday has the most products ordered while Tuesday and Wednesday have the least. 

Column {data-width=350} 
-----------------------------------------------------------------------
### Histogram of Time of Day Order for Saturday

```{r}



tod_order <-instacart %>%
  filter(order_dow == 0) %>%
  select(order_id, order_hour_of_day, order_dow) %>%
  mutate(order_dow = case_when(
    order_dow == 0 ~ "Saturday")) 

tod_order %>%
    plot_ly(x = ~order_hour_of_day, type = "histogram")
```
This histogram looks at the distribution of orders based on time of day. Most purchases occured in the late morning and early afternoon. 

